---
title: "A UN report on the relationships between GDP and Life exp"
author: "Faezeh"
date: "2023-05-25"
output: html_document
---


<!-- In the context of R Markdown and knitr (an R package), a "chunk" refers to a specific section of code within an R Markdown document that can be executed and rendered. Chunks are denoted by a specific syntax and are used to include and evaluate R code within the document. -->

```{r setup, include=FALSE}
#with add  include=FALSE. code and output will not show in the results 
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages , include=FALSE} 
#with add  echo=FALSE. only the code will not show in the results 
library(tidyverse)

```


This report was prepared to the attnetionof the United Nations. It analyzes the relation between a country's GDP, its life expectancy and CO2 emissions. Our goal is to determine to what gedree a country's econoic strenght or weakness may be related to its ublic health status and impact on climate population. We hypothesize that both life aexpectancy and CO2 emissions increase with a country's GDP.

```{r load_date, include =FALSE}
gapminder_1997 <- read_csv ("Data/gapminder_1997.csv")
```

```{r gdp_lifeexp_1997, echo=FALSE } 
ggplot (data =gapminder_1997) +
  aes ( x= gdpPercap, y= lifeExp,color=continent, size=pop/1000000)+
  geom_point()+
  labs(x= "GDP per capital", y= "Life of expectancy",
       title="Do peaple in wealthy countries life longer?",
       size="population [in million]")
```

```{r , include=FALSE}
nCountries <- gapminder_1997 %>% select(country) %>% n_distinct()
#this line count number of the country
#minGDP <- gapminder_1997 %>%  summarise(min(gdpPercap)) %>% pull() %>% round(,5)
#maxGDP <- gapminder_1997 %>%  summarise(max(gdpPercap)) %>% pull() %>% round(,5)

minGDP <- gapminder_1997 %>%  summarise(round(min(gdpPercap))) %>% pull()
maxGDP <- gapminder_1997 %>%  summarise(round(max(gdpPercap))) %>% pull() 
```

The above plot shows the relationship between GDP per capital and life expectancy fot a total of `r nCountries` countries. For this set of countries, econimic ealth ranged from a minimum of USD `r minGDP` to a maximum of USD `r maxGDP` per capita.

<!-- define table -->
<!-- Way1 -->
|HEDEAR 1| HEADER 2|
|--------|--------|
|row 1, column 1|row 1, column 2|
|row 2, column 1|row 2, column 2|

<!-- Way2 -->
```{r kable_table , echo=FALSE}
library(knitr)
gapminder_1997 %>% 
  filter(continent == "Oceania") %>% 
  kable()


```

